Towards a free/open-source universal-dependency treebank for Kazakh

### 2015-06-20 2015-turklang-kazdep/paper.tex
hargle
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60895 72bbbca6-d526-0410-a7d9-f06f51895060
refs
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60896 72bbbca6-d526-0410-a7d9-f06f51895060

This article describes the work towards the development of a dependency treebank for Kazakh, a
Turkic language spoken in Central Asia.
Despite its status as a \emph{core} Turkic
language, little computational-linguistic research has been published on syntactic
parsing for Kazakh.
A valuable resource in the study of syntactic parsing is
a treebank---a corpus of parsed text containing gold-standard syntactic annotation.

Freely available treebanks exist for many languages, such as large languages like Finnish (x,y) 
and Polish (xxx) and smaller languages like Irish \parencite{Lynn12}. To our knowledge only one treebank
exists for another language, Turkish \parencite{Oflazer03}, which is unfortunately not freely available.

>>>>

This article describes work towards the development of a dependency treebank for Kazakh, a Turkic language spoken in Central Asia and Europe.
Despite its status as a \emph{core} Turkic
language, little computational-linguistic research has been published on syntactic
parsing for Kazakh.
A valuable resource in the study of syntactic parsing is
a treebank---a corpus of parsed text containing gold-standard syntactic annotation.

Freely available treebanks exist for many languages, such as large languages like Finnish \parencite{haverinen2013tdt,voutilainen11} 
and Polish (xxx) and smaller languages like Irish \parencite{Lynn12}. To our knowledge only one treebank
exists for another language, Turkish \parencite{Oflazer03}, which is unfortunately not freely available.
